---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scielor

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/njahn82/scielor.svg?branch=master)](https://travis-ci.org/njahn82/scielor)
<!-- badges: end -->

The goal of scielor is to interface SciELO (<https://www.scielo.org/>) and its 
    open access collections.

## Installation

You can install the released version of scielor using devtools

``` r
devtools::install_github("njahn82/scielor")
```

## Example

Search SciELO

```{r}
scielo_search_all(list(q = "dengue"))
```

Return facets for whole SciELO content

```{r}
scielo_search_all(list(q = "dengue"), facet = TRUE)
```


## More about searching SOLR endpoints?

This package makes use of the package [solrium: General Purpose R Interface to 'Solr'](https://cran.r-project.org/web/packages/solrium/index.html) from [rOpenSci](https://ropensci.org/). 

## Contributing 

Please note that the 'scielor' project is released with a
  [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
